\documentclass[]{pubudu-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Pubudu}{Dissanayake}{ \urlstyle{same}\url{http://pubudu08.github.io} \\
\href{mailto:pubudu08@gmail.com}{pubudu08@gmail.com} | 0403113048
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Australian National}
\subsection{University}
\descript{Master of Computing}
\location{Specialized in Artificial Intelligence and Human Computer Interface \\ 2017 | Canberra, ACT}
\sectionsep

\subsection{University of Westminster}
\descript{BEng.(Hon) Software Engineering}
\location{2013 | London, UK}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/pubudu08}{\custombold{pubudu08}} \\
LinkedIn://  \href{https://www.linkedin.com/in/pubududissanayake/}{\custombold{pubududissanayake}} \\
Twitter://  \href{https://twitter.com/geekinaction}{\custombold{@GeekInAction}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Artificial Intelligence \\
Bio-inspired Computing  \\
Document Analysis  \\
Formal Methods in Software Engineering  \\
HCI Design and Evaluation \\
System Engineering \\
Managing Software Projects \\
Software Construction \\
Software Architecture and Human Brain\\
\sectionsep

\subsection{Undergraduate}
Algorithms and Data Structures\\
Information And Data Modelling\\
Software Engineering Principles\\
Computational Intelligence\\
Database Design And Practice\\
Advance Web Development \\
Real Time Embedded Systems \\
Project Management\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 5000 lines:}
Java \textbullet{}   Python \textbullet{} JavaScript \textbullet{} Matlab \\
\location{Over 1000 lines:}
Android \textbullet{} Matlab \textbullet{} CSS \textbullet{} HTML \textbullet{} R \\
SQL \textbullet{} \Csh{} \\
\location{Familiar:}
AngularJS 2+ \textbullet{} JAX-RS \textbullet{} JAX-WS \textbullet{} Spring \\
MySQL \textbullet{} JUnit \textbullet{} TensorFlow \textbullet{} Keras \\ 
OSGi \textbullet{} SOAP \textbullet{} Git \textbullet{} JQuery, \textbullet{} TypeScript \\
Jenkins CI 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{WSO2 Inc}
\descript{| Software Engineer }
\location{ 2013 - 2015 | Colombo, Sri Lanka}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Actively involved in development of WSO2 Carbon server (Kernel) and WSO2 Application Server.\item Researched and Developed features based on OSGi, XML/JSON and integrated with SOAP and REST services. \item Developed proof of concepts and applications of advanced complex scopes, such as Session Replication and Session
Persistence \item As a Full-stack developer - wrote and reviewed code for JavaScript, Java APIs for RESTful Web Services  \item Tested mission-critical firmware and software on a new product deployment team \item Developed and maintained automated tests in Java for regression testing. \item Practiced Agile in 2 week sprints with 8 other developers. \item All code was reviewed, perfected, and pushed to production.
\end{tightemize}
\sectionsep

\runsubsection{99X Technologies}
\descript{| Software Engineering Intern }
\location{ 2011 – 2012 | Colombo, Sri Lanka}
\begin{tightemize}
\item Developed, and managed a desktop and web based software pipeline for time management of a corporate Norwegian ISV. \item Practiced Agile in 2 week sprints with 10 other developers.\item All code was reviewed, perfected, and pushed to production using SVN.\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{ContExtractor}
\descript{| A Simple Search engine}
Developed a search engine based on Apache lucene and evaluated by using trec eval with test collections.
\sectionsep

\runsubsection{PixelatedSearch engine}
\descript{| Single Agent search Problem}
Designed, developed, and delivered an engine consists with uninformed and informed search strategies for the graphsearch
algorithm, In particular Breadth-First Search, Iterative Deepening Search, A* and MiniMax as an adversarial search
for two-player game.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2013	     & Upper Second Class Honours, UoW\\

\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Societies and Volunteer Experience} 

\begin{tabular}{rll}
2016 	& Mentor, SET4ANU, ANU \\
2016    & Photography Editor, Woroni - Student News paper, ANU\\
2016    & Member, ANU Computer Science Students' Association\\

\end{tabular}
\sectionsep
\section{Referees available upon request} 

\end{minipage} 
\end{document}